Meta-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-01-06 analysis/Stud1_a.qmd
quick changes

- Giulia
  - note: anx_21 , tas20_21 are attention checks

@@

df11a <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20, starts_with(c("MAIA", "TAS20", "DEP", "ANX")),  -ANX_21, -TAS20_21) |>
  mutate_all(as.numeric) |>
  rename(
    Age = AGE, Gender = GENDER,
    Heart = IAS_ACC_1, Hungry = IAS_ACC_2, Breathing = IAS_ACC_3, Thirsty = IAS_ACC_4,
    Urinate = IAS_ACC_5, Defecate = IAS_ACC_6, Taste = IAS_ACC_7, Vomit = IAS_ACC_8, Sneeze = IAS_ACC_9,
    Cough = IAS_ACC_10, Temp = IAS_ACC_11, Sex_arousal = IAS_ACC_12, Wind = IAS_ACC_13, Burp = IAS_ACC_14,
    Muscles = IAS_ACC_15, Bruise = IAS_ACC_16, Pain = IAS_ACC_17, Blood_Sugar = IAS_ACC_18,
    Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_21, Itch = IAS_ACC_22
  ) |>
   mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender %in% c(3, 5) ~ "Other",
    Gender == 4 ~ "NA"
  )) |> ## compute dimensions for the TAS
  mutate(TAS_DIF = TAS20_1 + TAS20_3 + TAS20_6 + TAS20_7 + TAS20_9 + TAS20_13 + TAS20_14,
         TAS_DDF = TAS20_2 + (1-TAS20_4) + TAS20_11 + TAS20_12 + TAS20_17,
         TAS_EOT = (1-TAS20_5) + TAS20_8 + (1-TAS20_10) + TAS20_15 + TAS20_16 + (1-TAS20_18) + (1-TAS20_19) + TAS20_20)

@@

- **Sample 1a**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 1, downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2[c("Age", "Gender")], age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5_attention, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7a**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7b**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7c**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7c, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10a**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10b**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10c**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10c, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 11a**: Data from [Giulia's (2024)](https://osf.io/49wbv) study , included `r report::report_participants(df11a, age = "Age", sex = NA, gender = "Gender")`
- **Sample 11b**: Data from [Giulia] study , included `r report::report_participants(df11b, age = "Age", sex = NA, gender = "Gender")`

>>>>

- Poreiro et al., 
  - Study 1: https://osf.io/49wbv
  - Study 2: unpublished

@@

df11a <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20, starts_with(c("MAIA", "TAS20", "DEP", "ANX")),  -ANX_21, -TAS20_21) |> #anx_21 , tas20_21 are attention checks
  mutate_all(as.numeric) |>
  rename(
    Age = AGE, Gender = GENDER,
    Heart = IAS_ACC_1, Hungry = IAS_ACC_2, Breathing = IAS_ACC_3, Thirsty = IAS_ACC_4,
    Urinate = IAS_ACC_5, Defecate = IAS_ACC_6, Taste = IAS_ACC_7, Vomit = IAS_ACC_8, Sneeze = IAS_ACC_9,
    Cough = IAS_ACC_10, Temp = IAS_ACC_11, Sex_arousal = IAS_ACC_12, Wind = IAS_ACC_13, Burp = IAS_ACC_14,
    Muscles = IAS_ACC_15, Bruise = IAS_ACC_16, Pain = IAS_ACC_17, Blood_Sugar = IAS_ACC_18,
    Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_21, Itch = IAS_ACC_22
  ) |>
   mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender %in% c(3, 5) ~ "Other",
    Gender == 4 ~ "NA"
  )) |> ## compute dimensions for the TAS
  mutate(TAS_DIF = TAS20_1 + TAS20_3 + TAS20_6 + TAS20_7 + TAS20_9 + TAS20_13 + TAS20_14,
         TAS_DDF = TAS20_2 + (1-TAS20_4) + TAS20_11 + TAS20_12 + TAS20_17,
         TAS_EOT = (1-TAS20_5) + TAS20_8 + (1-TAS20_10) + TAS20_15 + TAS20_16 + (1-TAS20_18) + (1-TAS20_19) + TAS20_20)

@@

- **Sample 1a**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 1, downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2[c("Age", "Gender")], age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5_attention, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7a**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7b**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7c**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7c, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10a**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10b**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10c**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10c, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 11a**: Data from [Giulia's (2024)](https://osf.io/49wbv) study , included `r report::report_participants(df11a, age = "Age", sex = NA, gender = "Gender")`
- **Sample 11b**: Data from [Giulia] study , included `r report::report_participants(df11b, age = "Age", sex = NA, gender = "Gender")`
